---
output: github_document
---

[![Travis build status](https://travis-ci.org/wlandau/drake.hasty.svg?branch=master)](https://travis-ci.org/wlandau/drake.hasty)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Hasty mode for the drake R package

Hasty mode is [`clustermq`](https://github.com/mschubert/clustermq) parallelism with all of `drake`'s storage and reproducibility guarantees stripped away. 

## Install

```{r installhasty, eval = FALSE}
library(remotes)
install_github("wlandau/drake.hasty")
```

## Use

```{r introhasty, eval = FALSE}
library(drake.hasty)
load_mtcars_example()
make(my_plan, parallelism = backend_hasty, jobs = 2)
```

## Drawbacks

- **DRAKE NO LONGER PROVIDES EVIDENCE THAT YOUR WORKFLOW IS TRUSTWORTHY OR REPRODUCIBLE. [THE CORE SCIENTIFIC CLAIMS](https://github.com/ropensci/drake#reproducibility-with-confidence) ARE NO LONGER VALID.**
- There is no cache. You need to write code to store your own targets. The `hasty_build` argument to `make()` and the `default_hasty_build()` function may help you get started.

## Advantages

- There is no overhead from storing and checking targets, so hasty mode runs much faster than `drake`'s standard modes.
- `drake` still builds the correct targets in the correct order, waiting for dependencies to finish before advancing downstream.

