---
output: github_document
---

[![stability-experimental](https://img.shields.io/badge/stability-experimental-orange.svg)](https://github.com/emersion/stability-badges#experimental)
[![Travis build status](https://travis-ci.org/wlandau/drake.hasty.svg?branch=master)](https://travis-ci.org/wlandau/drake.hasty)
[![Test coverage](https://codecov.io/github/wlandau/drake.hasty/coverage.svg?branch=master)](https://codecov.io/github/wlandau/drake.hasty?branch=master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(drake.hasty)
```

# Hasty mode for the drake R package

Hasty mode is accelerated execution with all of `drake`'s storage and reproducibility guarantees stripped away. For experimentation only. Use at your own risk.

## Drawbacks

1. **DRAKE NO LONGER PROVIDES EVIDENCE THAT YOUR WORKFLOW IS TRUSTWORTHY OR REPRODUCIBLE. [THE CORE SCIENTIFIC CLAIMS](https://github.com/ropensci/drake#reproducibility-with-confidence) ARE NO LONGER VALID.**
2. There is no cache, so 
    1. You need to write code to store your own targets (in your targets' commands or `config$hasty_build()`), and
    2. `knitr`/`rmarkdown` reports with calls to `loadd()`/`readd()` will no longer work properly as pieces of the pipeline.

## Advantages

1. Hasty mode is a sandbox. By supplying a `hasty_build` function to your `drake_config()` object, you can experiment with different ways to process targets.
2. There is no overhead from storing and checking targets, so hasty mode runs much faster than `drake`'s standard modes.
3. You still have scheduling and dependency management. `drake` still builds the correct targets in the correct order, waiting for dependencies to finish before advancing downstream.

## Installation

```{r installhasty, eval = FALSE}
library(remotes)
install_github("ropensci/drake")
install_github("wlandau/drake.hasty")
```

## Usage

We begin with a `drake` project.

```{r beginhasty}
library(drake.hasty)
plan <- drake_plan(x = rnorm(100), y = mean(x), z = median(x))

plan
```

Create a `drake_config()` object from your workflow.

```{r introhasty, eval = FALSE}
config <- drake_config(plan, parallelism = backend_hasty)
```

You can increase speed even more with some lesser-known `drake_config()` options.

```{r hastyconfig}
config <- drake_config(
  plan,
  parallelism = backend_hasty,
  cache = storr::storr_environment(),
  skip_imports = TRUE,
  session_info = FALSE,
  skip_safety_checks = TRUE
)
```

Next, supply a function to build individual targets. Feel free to borrow from `default_hasty_build()`.

```{r hastybuild}
config$hasty_build <- default_hasty_build

config$hasty_build
```

Finally, run the project. For the fastest execution, set `skip_imports` to `TRUE`

```{r hastyrun1}
make(config = config)
```

There is no caching or checking in hasty mode, so your targets are never up to date.

```{r hastyrun2}
make(config = config)
```

If you have `clustermq` installed, you can use parallel computing.

```{r hastyrun3}
# Use 2 persistent workers.
config$jobs <- 2

# See https://github.com/mschubert/clustermq for more options.
options(clustermq.scheduler = "multicore")

make(config = config)
```
