---
output: github_document
---

[![stability-experimental](https://img.shields.io/badge/stability-experimental-orange.svg)](https://github.com/emersion/stability-badges#experimental)
[![Travis build status](https://travis-ci.org/wlandau/drake.hasty.svg?branch=master)](https://travis-ci.org/wlandau/drake.hasty)
[![Test coverage](https://codecov.io/github/wlandau/drake.hasty/coverage.svg?branch=master)](https://codecov.io/github/wlandau/drake.hasty?branch=master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(drake.hasty)
```

# Hasty mode for the drake R package

Hasty mode is accelerated execution with all of `drake`'s storage and reproducibility guarantees stripped away. For experimentation only. Use at your own risk.

## Drawbacks

1. **DRAKE NO LONGER PROVIDES EVIDENCE THAT YOUR WORKFLOW IS TRUSTWORTHY OR REPRODUCIBLE. [THE CORE SCIENTIFIC CLAIMS](https://github.com/ropensci/drake#reproducibility-with-confidence) ARE NO LONGER VALID.**
2. By default, the cache is not used, so 
    1. You need to write code to store your own targets (in your targets' commands or `config$hasty_build()`), and
    2. `knitr`/`rmarkdown` reports with calls to `loadd()`/`readd()` will no longer work properly as pieces of the pipeline.

## Advantages

1. Hasty mode is a sandbox. By supplying a `hasty_build` function to your `drake_config()` object, you can experiment with different ways to process targets.
2. There is no overhead from storing and checking targets, so hasty mode runs much faster than `drake`'s standard modes.
3. You still have scheduling and dependency management. `drake` still builds the correct targets in the correct order, waiting for dependencies to finish before advancing downstream.

## Installation

```{r installhasty, eval = FALSE}
library(remotes)
install_github("ropensci/drake")
install_github("wlandau/drake.hasty")
```

## Basic usage

We begin with a `drake` project.

```{r beginhasty}
library(drake.hasty)
plan <- drake_plan(x = rnorm(100), y = mean(x), z = median(x))

plan
```

First, create a `drake_config()` object from your workflow.

```{r introhasty}
config <- drake_config(plan)
```

You really only need the `plan`, `schedule`, and `envir` slots of `config`. Feel free to create them yourself.

```{r minimalconfig}
config <- list(
  plan = config$plan,
  schedule = config$schedule,
  envir = config$envir
)
```

Then run the project.

```{r hastyrun1}
hasty_make(config = config)
```

By default, there is no caching or checking in hasty mode, so your targets are never up to date.

```{r hastyrun2}
hasty_make(config = config)
```

## Parallel and distributed computing

If you have the [`clustermq`](https://github.com/mschubert/clustermq) package installed, you can use parallel and distributed computing.

```{r hastyrun3}
# Use 2 persistent workers.
config$jobs <- 2

# See https://github.com/mschubert/clustermq for more options.
options(clustermq.scheduler = "multicore")

hasty_make(config = config)
```

## Custom build functions

You can customize how each target gets built. By default, `hasty_build_default()` is used.

```{r hastybuilddefault}
hasty_build_default
```

But there is another built-in function that also stores the targets to `drake`'s cache.

```{r hastybuildstore}
hasty_build_store
```

To use it, simply add the build function and a [`storr`](https://github.com/richfitz/storr) cache to `config` and run `hasty_make()`.

```{r usehastybuild}
config$hasty_build <- hasty_build_store
config$cache <- storr::storr_rds(tempfile())
hasty_make(config = config)
```

Now you can read targets from the cache.

```{r hastyread}
readd(z, cache = config$cache)
```

Similarly, you can write your own custom build functions for `config$hasty_build`.

```{r hastycleanup, echo = FALSE}
drake::clean(destroy = TRUE)
```
